---
title: 'Prostate Cancer Data Study'
author: "Se Yoon Lee, Peng Zhao, Debdeep Pati, and Bani Mallick"
output:
  html_document:
    df_print: paged
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**_NOTE:_** Objective of this code is to observe a tail-robustness  property (Carvalho, 2010, Biometrika) of a prior under a sparse normal mean model;
$$ \textbf{y} = \beta + \sigma\epsilon, \quad \epsilon \sim \mathcal{N}_p(\text{0}, \textbf{I}_p), \quad \beta \text{ is sparse}$$
where $\textbf{y} =(y_1, \cdots, y_p)^{\top} \in \mathbb{R}^p$ is responses that is downloadable from $\textsf{R}$ package $\textsf{sda}$. Refer to Section 6 in the main paper for a detail. 

An empirical way to check a tail-robustness property is as follows: first, plot ordered-pairs $\{(y_j,\widehat{\beta}_j)\}_{j=1}^p$ on the $\mathbb{R}^2$-plane, and then, see whether a reversed-S-shaped curve is formed by the pairs (See the left panel in Figure 5 in the main paper).


Install library packages
```{r}
library("ggplot2")
library("horseshoe") # by Stephanie van der Pas
library("MASS")
library("readr")
library("knitr")
library("compiler")
```

Bring external functions (To implement reviewers should set directory by setwd().)
```{r include=FALSE}
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
source("external_functions/horseshoe_van_der_pas.R") # this function is the same with horseshoe function in library(horseshoe)
source("external_functions/GLT_prior.R")
horseshoe_van_der_pas = cmpfun(horseshoe_van_der_pas)
GLT_prior = cmpfun(GLT_prior)
```


Simulation environment (We used (nmc,burn,thin) = (10000,10000,100) as a default.)
```{r}
seed.index = 1
nmc = 5000
burn = 5000
thin = 50
```

Decide number of genes to be considered.

**_NOTE:_** To see the collapsing behavior of the Horseshoe, use 
$p$ to be larger than $200$ genes. The maximum number of genes $p$ is $6,033$. As $p$ gets larger, posterior computation will take commensurably tremendously longer time.
```{r}
p = 200 # number of genes (Maximum is 6033)
```


Import prostate cancer data ( Users should set the directory by setwd() )
```{r include=FALSE}
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
load("prostate cancer data/prostz.RData")
y = prostz[1:p]
X = diag(p)
```


# 1. The Horseshoe prior
```{r echo=TRUE}
res = horseshoe_van_der_pas(y = y, X = X, method.tau = "halfCauchy", method.sigma = "Jeffreys", burn = burn, nmc = nmc, thin = thin) 

# burning & thinning
thined.beta.vec.HS = res$BetaSamples
post.mean.beta.HS = rowMeans(thined.beta.vec.HS)
```

# 2. The GLT prior
```{r echo=TRUE}
res = GLT_prior(y = y, X = X, BCM_sampling =  FALSE, burn = burn, nmc = nmc, thin = thin) 
  
# burning & thinning
thined.beta.vec.GLT = res$beta.vec
post.mean.beta.GLT = rowMeans(thined.beta.vec.GLT)
```



Display $p$ ordered-pairs $\{(y_j,\widehat{\beta}_j)\}_{j=1}^p$ on the $\mathbb{R}^2$-plane
```{r echo=FALSE}
# Horseshoe prior
beta.mean.HS = as.data.frame(post.mean.beta.HS)
beta.mean.HS$numberofgenes = p
beta.mean.HS$color = "red"
beta.mean.HS$prior = "HS"
names(beta.mean.HS)[1] = "beta.mean"
# GLT prior
beta.mean.GLT = as.data.frame(post.mean.beta.GLT)
beta.mean.GLT$numberofgenes = p
beta.mean.GLT$color = "blue"
beta.mean.GLT$prior = "GLT"
names(beta.mean.GLT)[1] = "beta.mean"
# Data
prostz.data = as.data.frame(y)
temp.df.beta = rbind(beta.mean.HS,beta.mean.GLT)
temp.df.y = rbind(prostz.data,prostz.data)
temp.df.beta.y = cbind(temp.df.beta, temp.df.y)
res = ggplot(temp.df.beta.y, aes(prior) ) +
  geom_point(aes(x = y,y = beta.mean, colour = prior)) +
  xlim(-5,5) + ylim(-5, 5) +
  xlab("y") + ylab(expression(paste(hat(beta)))) +
  geom_abline(intercept = c(0,0), slope = c(0,1), 
              colour = c("red","blue"),linetype = c(1,2)) +
  theme(axis.text=element_text(size=20),
        legend.text=element_text(size=20),
        legend.title=element_text(size=20),
        axis.title=element_text(size=20,face="bold"))
res
```

